Flattering Advice: Avoiding Disappointment as a Driver of Gender Discrimination

### 2024-01-16 manuscript/manuscript.Rmd
Revised on Jan 16 by Amanda

```{r setup, include=FALSE}
library(magrittr)

@@

```{r}
library("papaja")
# Fit linear regression model
study1_advice <- study1_advice %>% dplyr::mutate(ExpShow = ifelse(Condition == 'E',1,0))

model1 <- lm(Guess ~ Gender + count, data = study1_time1)
model1_apa <- apa_print(model1)
```

@@

```{r study1regs}
study1_advice <- study1_advice %>% dplyr::mutate(Treatment = factor(Treatment, levels = c('Low', 'High')))

@@

ggplot(df_exp, aes(x = Performance, y = avg_hardGroup, color = Gender)) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"),se = FALSE) +
  geom_smooth(data = df_none, aes(x = Performance, y = avg_hardGroup),
              method = "glm", method.args = list(family = "binomial"), color = "grey", se = FALSE) +
  scale_color_manual(values = c("red", "#4169E1", "grey"),
                     labels = c("Female + Expectations", "Male + Expectations", "Expectation Hidden")) +
  scale_y_continuous(name = "P(Compete Against High Performance)",
                     labels = scales::percent,
                     expand = c(0, 0)) +
  scale_x_continuous(name = "Performance",
                     expand = c(0, 0),
                     breaks = seq(0, 10, 2)) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "grey"),
        legend.position = "bottom",
        legend.title = element_blank(),
        legend.key.size = unit(1.2, "lines"),
        legend.text = element_text(size = 12),
        plot.title = element_text(hjust = 0.5, size = 20))
```

@@

modelsummary::modelsummary(list(`(1)` = lm(bonus ~ AdviseeCondition + AdviseeScore , data = study1_time3),
                                `(2)` = lm(Bet ~ Gender + AdviseeScore , data = study1_time3),
                                `(3)` = lm(Adopt ~ Gender + GiverCondition + Advice, data = study1_time3),
                                `(4)` = lm(Adopt ~ Gender + GiverCondition + Advice + Gender*GiverCondition + GiverCondition*Advice + Gender*Advice, data = study1_time3)),
                           vcov = c("classical", "classical","classical","classical"),
                            coef_map = c("AdviseeScore" = "Performance",
                                         "AdviseeConditionHigh" = "High Expectation",
                                        "GenderMale" = "Advisee Male",
                                        "GenderMale:GiverCondition" = "Expectation x Male",
                                        "GiverCondition" = "Expectation Shown",
                                        "Advice1" = "Advice: High Performer",
                                        "GenderMale:Advice1" = "Advice: High Performer x Male",
                                        "GiverCondition:Advice1" = "Expectation x Advice: High Performer",
                                        "(Intercept)" = "Constant"),
                           stars = T,
                           gof_map = list(list('raw' = 'nobs', 'clean' = 'N', 'fmt' = 0)),
                           caption = "Column 1 displays the actual bonus based on the performance and whether the participant is primed with high expectations. Column 2 displays whether the participant chooses to compete against a high-performance group based on performance and gender of the participants. Columns 3 and 4 display the chance of adopting the advice based on the gender of the participants, whether the advisee sees expectations, and whether the advice is to compete against high performers. The former considers only the main effect, while the latter also includes the interactive effect.")

@@

To determine whether flattering advice is truly costly, however, we need
to examine the outcome of the advisees. In particular, they could ignore flattering
advice, recognizing it as such and thus failing to adhere to it.

<!-- David: Let's turn the regression you discussed below into a column of the Table above --> 
<!-- Amanda: Can we create a new table for analyzing time 3 data? Because the variables are different from the previous table, the current table might be difficult to read with new columns. Additionally, the new analysis is only focused on fr advice shown to its target, not all 10,000 advice. It might be vonfusing if we put them together. --> 
<!-- David: Also, one more suggestion for an analysis: let's look at whether Advisees followed the recommendation they received as an other linear probability model (1/0). I would suggest predictors of whether it's the High Performer group, whether the adviser saw expectations, the gender of the advisee. Also, another model that has the two-way interaction for all of those. We may not end up reporting this, but I would be curious to see. -->

## Discussion
When the quality of a decision is not dependent on someone's expectations,
advice should not be moved by whether an adviser is aware of the advisees
expectations. However, consistent with our account that advisers consider the
belief utility of the advisee and want to flatter, rather than disappoint them,
we find that displaying expectations to advisers does matter.
Specifically, we found that men underestimate their score on a mathematics test
less than do women. When these expectations are displayed to advisers, they
are more likely to tell men to compete against the High Performer group.
Notably, this is bad advice: men whose advisers observed their expectations
got worse advice as a result.

@@

study2_time1 <- readRDS(here::here("Data/Study2_time1.Rds"))
study2_time1_200 <- readRDS(here::here("Data/Study2_time1_200.Rds"))
study2_time2 <- readRDS(here::here("Data/Study2_time2.Rds"))
study2_time3 <- readRDS(here::here("Data/Study2_time3.Rds"))

@@

We recruited 300 participants from Prolific and invited them to upload photos of
themselves (selfies) to be rated by other participants on
attractiveness.
`r scales::comma(dim(study2_time1[study2_time1$gender == 'Male',])[1])`
men and
`r scales::comma(dim(study2_time1[study2_time1$gender == 'Female',])[1])`
women agreed to do so and uploaded pictures that adhered to our
instructions (e.g., did not include other people). We selected the
first 100 photos from women to arrive at a gender-balanced sample
($M_{\text{Age}}$ = `r mean(study2_time1_200$age)` years).
Participants were informed that their selfies would be randomly grouped with
those of nine other participants of their gender and ranked in terms of attractiveness
by a group of new Prolific participants of the opposite gender.
They then guessed their rank (unincentivized) and the survey concluded
with demographic questions **David: or did we start with those?**

Next, we recruited a new, gender-balanced sample for the role
of advisers. `r scales::comma(dim(study2_time2)[1])`
participants from Prolific ($M_{\text{Age}}$ =
`r mean(study2_time2$age)` years;
`r round(mean(study2_time2$gender == "Female")*100, 2)`% Female) started by
providing demographic information, then were matched to a group of the opposite
gender. They then ranked participants from most to least attractive using a
drop-down menu next to each picture.
<!-- David: wasn't there something with participants selecting the same rank more -->
<!-- than once, and we dropped people who did that? Or were we able to solve this -->
<!-- and it happened only during a pilot? -->
After submitting their ratings, they saw the photo of the participant they
had ranked as the 7th most attractive (i.e., the 4th least attractive). They
were reminded of the rank they had given to that perso and informed
that this participant would be invited back and could earn a \$1 bonus if they
guessed their rank correctly. The rank was determined by the aggregate ratings
of all participants who had ranked this group. Their task was to give advice
to this participant about the rank they should bet on based on having observed
all ten selfies and their own assessment. We randomly assigned participants to
one of two incentivization schemes. In the "Accuracy" treatment, they received
a bonus identical to the advisee: \$1 if they guessed their rank correctly.
In the "Likeability" treatment, we informed them that they would be rated by
the advisee on a 5-point Likert scale for how likeable they thought they were.
Each point on the scale would translate to a bonus of 20 cents. They then
selected a rank that they would recommend the advisee to bet on.

@@

<!-- David: The treatment differences here are hard to see. The most salient feature -->
<!-- is the spike at 7th (which suggests no flattering advice), and the spike at 5. -->
<!-- Can we try a violin plot for the advised rank?  And maybe we can add a -->
<!-- dotted horizontal line at 7. This is would be consistent with what they said -->
<!-- just on the previous screen. So a good reference line. -->

```{r study2advice, fig.cap="Advice given to the 7th most attractive participants"}
library(dplyr)
library(ggplot2)

count <- study2_time2 %>%
  group_by(Condition) %>%
  summarize(number = dplyr::n())

advice_avg <- study2_time2 %>%
  group_by(Condition, Advice) %>%
  summarize(n = dplyr::n()) %>%
  dplyr::mutate(conditionCount = ifelse(Condition == 'Likable',count[count$Condition == 'Likable',]$number,count[count$Condition == 'Accurate',]$number)) %>%
  dplyr::mutate(percent = n/conditionCount*100) %>% 
  dplyr::select(Condition,Advice,percent)

# Create a facet plot with condition as the facet variable and gender as the line color
ggplot(advice_avg, aes(x = Advice, y = percent, color = Condition)) +
  geom_line(linewidth = 0.75)+
  scale_color_manual(values = c("#FFA500", "#4169E1"),
                      labels = c("Accurate", "Likable")) +
  scale_y_continuous(name = "% of participants") +
  scale_x_continuous(name = "Advised Rank",
                     breaks = seq(1, 10)) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "grey"),
        legend.position = "bottom",
        legend.title = element_blank(),
        legend.key.size = unit(1.2, "lines"),          
        legend.text = element_text(size = 12),
        plot.title = element_text(hjust = 0.5, size = 20))

@@

We begin by examining the prior beliefs of advisees who uploaded their selfies.
On average, men guessed they ranked `r round(mean(study2_time1[study2_time1$gender == "Male",]$Guess),2)` in their group of 10 and women guessed that they ranked
`r round(mean(study2_time1[study2_time1$gender == "Female",]$Guess),2)`.
Participants overall underestimate their attractiveness relative to the benchmark
average of 5.5. Moreover, women do so more than men
`r papaja::apa_print(t.test(Guess ~ gender, data = study2_time1, var.equal = T))$statistic`.
Notably, people's self-perceptions correlated strongly/weakly with the aggregate
ratings of the advisers (correlation coefficient & cor.test). However, there
was substantial heterogeneity in perceptions of attractiveness.
Of the 200 participants, XXX were ranked as 7th most attractive by at least one
adviser. On average,
men in this subset estimated they were ranked Xth and women estimated they were
ranked Xth (t-test).

<!-- David: Some stats to fill in above. I think this would be interesting to include -->
<!-- even though we don't make any predictions about this. -->

@@

```{r study2rating, fig.cap="The evaluation of advice givers"}

rating <- study2_time3 %>%
  group_by(Advice) %>%
  summarise(Likable = mean(likable), Warm = mean(warmAvg), Trust = mean(trustAvg))

ggplot(rating, aes(x = Advice)) +
  geom_line(aes(y = Likable, color = "Likable"), linewidth = 0.75) +
  geom_line(aes(y = Warm, color = "Warm"), linewidth = 0.75) +
  geom_line(aes(y = Trust, color = "Trust"), linewidth = 0.75) +
  scale_color_manual(values = c("Likable" = "#FFA500", "Warm" = "#4169E1", "Trust" = "grey"),
                      labels = c("Likable", "Warm", "Trust")) +
  scale_y_continuous(name = "Rating") +
  scale_x_continuous(name = "Advised Rank") +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "grey"),
        legend.position = "bottom",
        legend.title = element_blank(),
        legend.key.size = unit(1.2, "lines"),          
        legend.text = element_text(size = 12),
        plot.title = element_text(hjust = 0.5, size = 20))

@@

Finally, we examine whether flattering advice indeed leads to more positive evaluations of
advisers, or whether flattering advice is dismissed as insencere.
Following our preregistration, we average the ratings on likeability,
warmth,  friendliness, and good-naturedness to create a scale of likeability
($\alpha$ = XXX);
<!-- David: The draft had trustworthiness as part of this scale. -->
<!-- Can we just double-check against the preregistration? -->
<!-- And was Likeable part of that? -->
<!-- We might also want a name for the scale that isn't the same as one -->
<!-- of the items, though I'm not sure what. -->
<!-- Same for trustworthiness -- though that could simply be "Trust" -->
and we create a scale of trustworthiness by averaging the ratings of
trustworthiness and sincerity ($\alpha$ = XXX).

@@

As seen in Figure \@ref(fig:study2rating), we
found that advisees who suggested that the advisee was more attractive
(lower rank) were indeed rated as more likeable and warm (b = -0.109, p
\< .05; b = -0.133, p \< .001, respectively; See Columns 1 and 2 of Table \@ref(tab:study2regs)).
Interestingly, these benefits are not at the cost of being hypocritical;
advisers who recommend a more favorable rank are viewed as no less trustworthy
(Column 3 of Table \@ref(tab:study2regs)).

We were not powered to do a comparison across the two 
experimental groups and did not preregister such a difference.
<!-- David: But we still need to report warmth & trust across treatments. -->

@@

However, this flattering advice comes at a cost to advisees, who would do worse
if they followed it blindly, as we show in Study 1.
<!-- David: But not Study 2? I guess we're not sure yet? -->
Moreover, a desire to avoid disappointment also means that advisers have to
take into account the expectations of the advisee. 
We document that men are more optimistic about their performance than
women are. As a result, they receive more flattering advice and are more likely
to be told to aim higher. Notably, in the context of our experiment, this turns
out to be bad advice ex post.

>>>>

```{r setup, include=FALSE}
library(magrittr)
library(ltm)

@@

@@

```{r study1regs}
study1_advice <- study1_advice %>% dplyr::mutate(Treatment = factor(Treatment, levels = c('Low', 'High'))) %>%
  dplyr::mutate(ExpShow = ifelse(Condition == 'E',1,0))

@@

ggplot(df_exp, aes(x = Performance, y = avg_hardGroup, color = Gender)) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"),se = FALSE) +
  geom_smooth(data = df_none, aes(x = Performance, y = avg_hardGroup),
              method = "glm", method.args = list(family = "binomial"), color = "grey", se = FALSE) +
  scale_color_manual(values = c("#E74C3C", "#4169E1", "grey"),
                     labels = c("Female + Expectations", "Male + Expectations", "Expectation Hidden")) +
  scale_y_continuous(name = "P(Compete Against High Performance)",
                     labels = scales::percent,
                     expand = c(0, 0)) +
  scale_x_continuous(name = "Performance",
                     expand = c(0, 0),
                     breaks = seq(0, 10, 2)) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "grey"),
        legend.position = "bottom",
        legend.title = element_blank(),
        legend.key.size = unit(1.2, "lines"),
        legend.text = element_text(size = 12),
        plot.title = element_text(hjust = 0.5, size = 20))
```

@@

modelsummary::modelsummary(list(`(1)` = lm(bonus ~ AdviseeCondition + AdviseeScore, data = study1_time3 %>%
                                             dplyr::filter(GiverCondition == 1)),
                                `(2)` = lm(bonus ~ Gender + AdviseeScore, data = study1_time3 %>%
                                             dplyr::filter(GiverCondition == 1)),
                                `(3)` = lm(Adopt ~ Gender + GiverCondition + Advice, data = study1_time3),
                                `(4)` = lm(Adopt ~ Gender + GiverCondition + Advice + Gender*GiverCondition + GiverCondition*Advice + Gender*Advice, data = study1_time3)),
                           vcov = c("classical", "classical","classical","classical"),
                            coef_map = c("AdviseeScore" = "Performance",
                                         "AdviseeConditionHigh" = "High Expectation",
                                        "GenderMale" = "Advisee Male",
                                        "GenderMale:GiverCondition" = "Expectation x Male",
                                        "GiverCondition" = "Expectation Shown",
                                        "Advice1" = "Advice: High Performer",
                                        "GenderMale:Advice1" = "Advice: High Performer x Male",
                                        "GiverCondition:Advice1" = "Expectation x Advice: High Performer",
                                        "(Intercept)" = "Constant"),
                           stars = T,
                           gof_map = list(list('raw' = 'nobs', 'clean' = 'N', 'fmt' = 0)),
                           caption = "Column 1 displays the actual bonus based on the performance and whether the participant is primed with high expectations. Column 2 displays the actual bonus based on the performance and gender of the participant. Columns 3 and 4 display the chance of adopting the advice based on the gender of the participants, whether the advisee sees expectations, and whether the advice is to compete against high performers. The former considers only the main effect, while the latter also includes the interactive effect.")

@@

To determine whether flattering advice is truly costly, however, we need
to examine the outcome of the advisees. In particular, they could ignore flattering
advice, recognizing it as such and thus failing to adhere to it. Align with our prediction, participants who were primed with high expectations earned less when their expectations were conveyed to the advisers, although this result is only directional  (see Column 1 of Table \@ref(tab:study1time3)). Similarly, as shown in Column 2 of Table \@ref(tab:study1time3), Similarly, as shown in Column 2 of Table 1, we also found that male participants received less reward when their expectations were presented, even when their performance was the same. These findings suggest that flattering advice is not without consequences. Furthermore, our research indicates that because males are more likely to follow such advice (see Column 4 of Table \@ref(tab:study1time3), their tendency towards competition intensifies the cost of such advice.

<!-- David: Let's turn the regression you discussed below into a column of the Table above --> 
<!-- David: Also, one more suggestion for an analysis: let's look at whether Advisees followed the recommendation they received as an other linear probability model (1/0). I would suggest predictors of whether it's the High Performer group, whether the adviser saw expectations, the gender of the advisee. Also, another model that has the two-way interaction for all of those. We may not end up reporting this, but I would be curious to see. -->

<!-- Amanda: Can we create a new table for analyzing time 3 data? Because the variables are different from the previous table, the current table might be difficult to read with new columns. Additionally, the new analysis is only focused on fr advice shown to its target, not all 10,000 advice. It might be confusing if we put them together. -->

## Discussion
When the quality of a decision is not dependent on someone's expectations,
advice should not be moved by whether an adviser is aware of the advisees
expectations. However, consistent with our account that advisers consider the
belief utility of the advisee and want to flatter, rather than disappoint them,
we find that displaying expectations to advisers does matter.
Specifically, we found that men underestimate their score on a mathematics test
less than do women. When these expectations are displayed to advisers, they
are more likely to tell men to compete against the High Performer group.
Notably, this is bad advice: men whose advisers observed their expectations
got worse advice as a result. <!-- Amanda: Our findings suggest that males earned less than their female counterparts who scored the same as them, although the evidence is only directional. This could be attributed to the fact that males received more flattering advice and were more likely to adopt it, resulting in even worse outcomes.-->

@@

study2_time1 <- readRDS(here::here("Data/Study2_time1.Rds"))
study2_time1_200 <- readRDS(here::here("Data/Study2_time1_200.Rds"))
study2_time2 <- readRDS(here::here("Data/Study2_time2.Rds"))
study2_finalRank <- readRDS(here::here("Data/Study2_finalRank.Rds"))
study2_time3 <- readRDS(here::here("Data/Study2_time3.Rds"))

@@

We recruited 300 participants from Prolific and, after asking demographic questions, invited them to upload photos of
themselves (selfies) to be rated by other participants on
attractiveness. 
`r scales::comma(dim(study2_time1[study2_time1$gender == 'Male',])[1])`
men and
`r scales::comma(dim(study2_time1[study2_time1$gender == 'Female',])[1])`
women agreed to do so and uploaded pictures that adhered to our
instructions (e.g., did not include other people). We selected the
first 100 photos from women to arrive at a gender-balanced sample
($M_{\text{Age}}$ = `r mean(study2_time1_200$age)` years).
Participants were informed that their selfies would be randomly grouped with
those of nine other participants of their gender and ranked in terms of attractiveness
by a group of new Prolific participants of the opposite gender.
Lastly, they guessed their rank (unincentivized). **David: or did we start with those?**
<!-- Amanda: We started with demographic questions -->

Next, we recruited a new, gender-balanced sample for the role
of advisers. `r scales::comma(dim(study2_time2)[1])`
participants from Prolific ($M_{\text{Age}}$ =
`r mean(study2_time2$age)` years;
`r round(mean(study2_time2$gender == "Female")*100, 2)`% Female) started by
providing demographic information, then were matched to a group of the opposite
gender. They then ranked participants from most to least attractive using a
drop-down menu next to each picture. <!-- Amanda: We excluded data from participants who assigned the same rank to multiple selfies.-->
<!-- David: wasn't there something with participants selecting the same rank more -->
<!-- than once, and we dropped people who did that? Or were we able to solve this -->
<!-- and it happened only during a pilot? -->
<!-- Amanda: We did not catch this error in pilot, so we decided to use this as a manipulation check -->
After submitting their ratings, they saw the photo of the participant they
had ranked as the 7th most attractive (i.e., the 4th least attractive). They
were reminded of the rank they had given to that perso and informed
that this participant would be invited back and could earn a \$1 bonus if they
guessed their rank correctly. The rank was determined by the aggregate ratings
of all participants who had ranked this group. Their task was to give advice
to this participant about the rank they should bet on based on having observed
all ten selfies and their own assessment. We randomly assigned participants to
one of two incentivization schemes. In the "Accuracy" treatment, they received
a bonus identical to the advisee: \$1 if they guessed their rank correctly.
In the "Likeability" treatment, we informed them that they would be rated by
the advisee on a 5-point Likert scale for how likeable they thought they were.
Each point on the scale would translate to a bonus of 20 cents. They then
selected a rank that they would recommend the advisee to bet on.

@@

```{r}
library(dplyr)

TargetsUnique <- study2_time2 %>%
  dplyr::select(Target) %>%
  unique()

TargetsUnique <- merge(TargetsUnique,study2_finalRank, by.x = 'Target', by.y = 'QID7_Id')

@@

```{r study2advice, fig.cap="Advice given to the 7th most attractive participants"}

study2_time2 <- study2_time2 %>% dplyr::mutate(Advice = as.numeric(Advice))

ggplot(study2_time2, aes(x = Condition, y = Advice, fill = Condition)) +
    geom_violin(trim = FALSE) +
     scale_fill_manual(values = c("#E74C3C", "#4169E1"), labels = c("Accurate", "Likable")) +
  geom_hline(yintercept = 7, col = 'grey', linetype = 'dashed', linewidth = 0.7) +
  scale_y_continuous(name = "Advised Rank", breaks = seq(1, 10)) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "grey"),
        legend.position = "bottom",
        legend.title = element_blank(),
        legend.key.size = unit(1.2, "lines"),
        legend.text = element_text(size = 12),
        plot.title = element_text(hjust = 0.5, size = 20))

We begin by examining the prior beliefs of advisees who uploaded their selfies.
On average, men guessed they ranked `r round(mean(study2_time1[study2_time1$gender == "Male",]$Guess),2)` in their group of 10 and women guessed that they ranked
`r round(mean(study2_time1[study2_time1$gender == "Female",]$Guess),2)`.
Participants overall underestimate their attractiveness relative to the benchmark
average of 5.5. Moreover, women do so more than men
`r papaja::apa_print(t.test(Guess ~ gender, data = study2_time1, var.equal = T))$statistic`.
Notably, people's self-perceptions correlated strongly with the aggregate
ratings of the advisers (`r round(cor(study2_finalRank$Guess, study2_finalRank$finalRank),2)`, `r papaja::apa_print(cor.test(study2_finalRank$Guess, study2_finalRank$finalRank))$statistic`). However, there
was substantial heterogeneity in perceptions of attractiveness.
Of the 200 participants, `r length(unique(study2_time2$Target))` were ranked as 7th most attractive by at least one adviser. 
On average, men in this subset estimated they were ranked `r round(mean(TargetsUnique[TargetsUnique$gender == 'Male',]$Guess),2)`th and women estimated they were
ranked `r `round(mean(TargetsUnique[TargetsUnique$gender == 'Female',]$Guess),2)`th (`r papaja::apa_print(t.test(Guess ~ gender, data = TargetsUnique, var.equal = T))$statistic`).

@@

<!-- Amanda: How about this -->
```{r study2Rating, fig.cap="The evaluation of advice givers"}
# Load the necessary packages
library(ggplot2)
library(gridExtra)
library(dplyr)

study2_time3 <- study2_time3 %>% dplyr::mutate(Advice = as.factor(Advice))

# Create the first plot
plot1 <- ggplot(study2_time3, aes(x = Advice)) +
  geom_boxplot(aes(y = likable),position = position_dodge()) +
  scale_y_continuous(name = "Rating on Likability") +
  scale_x_discrete(name = "Advised Rank") +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "grey"),
        legend.position = "bottom",
        legend.title = element_blank(),
        legend.key.size = unit(1.2, "lines"),          
        legend.text = element_text(size = 12),
        plot.title = element_text(hjust = 0.5, size = 20))

# Create the second plot
plot2 <- ggplot(study2_time3, aes(x = Advice)) +
  geom_boxplot(aes(y = warmAvg),position = position_dodge()) +
  scale_y_continuous(name = "Rating on Warmth") +
  scale_x_discrete(name = "Advised Rank") +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "grey"),
        legend.position = "bottom",
        legend.title = element_blank(),
        legend.key.size = unit(1.2, "lines"),          
        legend.text = element_text(size = 12),
        plot.title = element_text(hjust = 0.5, size = 20))

# Combine the plots side by side
grid.arrange(plot1, plot2, ncol = 2)

@@

Finally, we examine whether flattering advice indeed leads to more positive evaluations of
advisers, or whether flattering advice is dismissed as insencere.
Following our preregistration, we average the ratings on likeability,
warmth,  friendliness, and good-naturedness to create a scale of likeability
($\alpha$ = `r cronbach.alpha(study2_time3[, 5:8])$alpha`);
<!-- David: The draft had trustworthiness as part of this scale. -->
<!-- Can we just double-check against the preregistration? -->
<!-- And was Likeable part of that? -->
<!-- We might also want a name for the scale that isn't the same as one -->
<!-- of the items, though I'm not sure what. -->
<!-- Same for trustworthiness -- though that could simply be "Trust" -->

<!-- Amanda: My bad. We only pre-reg that we will measure likable (single item) and warm (four items)" -->
<!-- I include trustworthiness here because it is part of that existing scale" -->

and we create a scale of trustworthiness by averaging the ratings of
trustworthiness and sincerity ($\alpha$ = `r cronbach.alpha(study2_time3[, 9:10])$alpha`).

@@

<!-- Amanda: How about the following picture? -->

```{r study2ratingByGroup, fig.cap="The Response to Different Advice"}

library(dplyr)
library(ggplot2)

study2_time3 <- study2_time3 %>% dplyr::mutate(Guess = as.numeric(Guess), Advice = as.numeric(Advice)) %>%
  dplyr::mutate(HorL = ifelse(Guess == Advice,0, ifelse(Guess > Advice, 1,-1))) %>%
  dplyr::mutate(HorL = as.factor(HorL)) %>% 
  dplyr::mutate(bonus = ifelse(bet == `Final Rank`,1,0))

ratings <- study2_time3 %>%
  group_by(HorL) %>%
  summarise(like = mean(likable), warmth = mean(warmAvg))

rating_table <- matrix(c(ratings$like,ratings$warmth), nrow = 2, byrow = TRUE, dimnames = list( c("Likable",'Warm'),c("Pessimistic", "Accurate", "Flattering")))

rating_df = as.data.frame.table(rating_table) %>%
  dplyr::rename( 'Condition'='Var1', 'Advice' ='Var2') %>%
  dplyr::mutate(Freq = round(Freq,2))

ggplot(rating_df, aes(x = Advice, y = Freq, fill = Condition)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = c("#E74C3C",'#4169E1')) +
  labs(x = "Advice", y = "Rating") +
  ggtitle('Response to Advice') +
  theme_bw() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "grey"),
        legend.position = "bottom",
        legend.title = element_blank(),
        legend.key.size = unit(1.2, "lines"),          
        legend.text = element_text(size = 12),
        plot.title = element_text(hjust = 0.5, size = 20)) +
  geom_text(aes(label = paste0(Freq), y = 0.5), position = position_dodge(width = 0.9), size = 2, color = 'white')

As seen in Figure \@ref(fig:study2Rating), we
found that advisees who suggested that the advisee was more attractive
(lower rank) were indeed rated as more likeable and warm (b = -0.109, p
\< .05; b = -0.133, p \< .001, respectively; See Columns 1 and 2 of Table \@ref(tab:study2regs)).
Interestingly, these benefits are not at the cost of being hypocritical;
advisers who recommend a more favorable rank are viewed as no less trustworthy
(Column 3 of Table \@ref(tab:study2regs)).

We were not powered to do a comparison across the two 
experimental groups and did not preregister such a difference. Indeed, we observed that advisers in the Accurate condition received higher ratings in both likable and warm dimensions (`r papaja::apa_print(t.test(likable ~ Condition, data = study2_time3, var.equal = T))$statistic`, and `r papaja::apa_print(t.test(warmAvg ~ Condition, data = study2_time3, var.equal = T))$statistic`, respectively). While the difference is not statistically significant, the results suggest that there may be an optimal range for the level of inflation.
<!-- David: But we still need to report warmth & trust across treatments. -->

@@

However, this flattering advice comes at a cost to advisees, who would do worse
if they followed it blindly, as we show in Study 1.

<!-- David: But not Study 2? I guess we're not sure yet? -->

<!-- Amanda: among 146 participants in time 3, only 25 guessed correctly. not enough variation-->
<!-- Nonetheless, participants received advice from accurate condition earned less (0.15 vs 0.2) -->

Moreover, a desire to avoid disappointment also means that advisers have to
take into account the expectations of the advisee. 
We document that men are more optimistic about their performance than
women are. As a result, they receive more flattering advice and are more likely
to be told to aim higher. Notably, in the context of our experiment, this turns
out to be bad advice ex post.
